Stateless Model Checking with Data-Race Preemption Points

### 2016-08-12 oopsla-16/overview.tex
minor tweak

We also identify the {\em minimal} and {\em maximal state space} for each test.
The {\em minimal state space} includes only thread switches arising from no preemptions (Figure~\ref{fig:id}, A).
The {\em maximal state space} is the one tested by SSS-MC: all statically-available PPs are enabled (Figure~\ref{fig:id}, D).
%However, should new data-race PPs be added during a test, the new maximal state space will be the one including those as well.
%% don't say this ^ -- because when you add dr pps, they add in pairs and there would be multiple maximals, at least until they each get explored and subseuqnetly add a pp of the other of the pair.

>>>>

We also identify the {\em minimal} and {\em maximal state space} for each test.
The {\em minimal state space} includes only thread switches arising from no preemptions (Figure~\ref{fig:id}(a)).
The {\em maximal state space} is the one tested by SSS-MC: all statically-available PPs are enabled (Figure~\ref{fig:id}(d)).
%However, should new data-race PPs be added during a test, the new maximal state space will be the one including those as well.
%% don't say this ^ -- because when you add dr pps, they add in pairs and there would be multiple maximals, at least until they each get explored and subseuqnetly add a pp of the other of the pair.
